---
title: "Analyzing the Impact on Stroke Risk"
author: "Minwoo Oh"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
geometry: left=0.5in,right=0.5in,top=0.5in,bottom=0.5in
urlcolor: blue
header-includes: \usepackage{subfig}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)
library(esquisse)
library(mosaic)
library(mosaicData)
library(dcData)
library(stringr)
```

# Set Directory and Call the Dataset

```{r}
brain_stroke <- read_csv("brain_stroke.csv")
head(brain_stroke)
tail(brain_stroke)
summary(brain_stroke)
```

# Creat Summary Table

```{r}
# Convert gender and stroke to factors with levels "Female" and "Male" for gender, and "0" and "1" for stroke
brain_stroke$gender <- factor(brain_stroke$gender, levels = c("Female", "Male"))
brain_stroke$stroke <- factor(brain_stroke$stroke, levels = c("0", "1"))

# Create a summary table
summary_table <- brain_stroke %>%
  group_by(gender, stroke) %>%
  summarise(count = n(), .groups = "drop")
```

# Bar Plot for Gender and Stroke

```{r}
# Bar plot for gender and stroke with counts and custom labels
ggplot(brain_stroke, aes(x = gender, fill = stroke)) +
  geom_bar(position = "dodge") +
  geom_text(data = summary_table, 
            aes(x = gender, y = count, label = count, group = stroke),
            position = position_dodge(width = 0.9), vjust = -0.25) +
  scale_fill_manual(values = c("grey", "red"),
                    labels = c("No Stroke", "Stroke"),
                    name = "Stroke") +
  labs(title = "Distribution of Stroke by Gender",
       x = "Gender",
       y = "Count") +
  theme_minimal()
```

# Box Plot for Age and Stroke

```{r}
# Box plot for age and stroke with custom labels
ggplot(brain_stroke, aes(x = stroke, y = age, fill = stroke)) +
  geom_boxplot() +
  scale_fill_manual(values = c("grey", "red"),
                    labels = c("No Stroke", "Stroke"),
                    name = "Stroke") +
  labs(title = "Boxplot of Age by Stroke Status",
       x = "Stroke Status",
       y = "Age") +
  theme_minimal()
```

# Box Plot for Age by Gender and Stroke

```{r}
# Summary statistics for age
summary(brain_stroke$age)
# Cross-tabulation of gender and stroke
table(brain_stroke$gender, brain_stroke$stroke)

# Boxplot of age by gender and stroke
ggplot(brain_stroke, aes(x = gender, y = age, fill = stroke)) +
  geom_boxplot() +
  scale_fill_manual(values = c("grey", "red"),
                    labels = c("No Stroke", "Stroke"),
                    name = "Stroke") +
  labs(title = "Boxplot of Age by Gender and Stroke Status",
       x = "Gender",
       y = "Age") +
  theme_minimal()
```

# T-Test for Age Difference between Genders

```{r}
# One-way ANOVA to test for age differences by gender and stroke
model <- aov(age ~ gender * stroke, data = brain_stroke)
summary(model)

# t-test for age between male and female within each stroke group
t_test_stroke_0 <- t.test(age ~ gender, data = subset(brain_stroke, stroke == "0"))
t_test_stroke_1 <- t.test(age ~ gender, data = subset(brain_stroke, stroke == "1"))

print(t_test_stroke_0)
print(t_test_stroke_1)
```

## For individuals without a stroke (t_test_stroke_0):
### P-value: 0.02914
> The p-value is less than 0.05, suggesting a statistically significant difference in age between genders for individuals without a stroke.

### Effect Size (Confidence Interval):
>The confidence interval (0.15 to 2.76) suggests that the true difference in means between females and males for individuals without a stroke is likely to fall between these values.

### Means:
>The mean age for females without a stroke is approximately 42.75.
The mean age for males without a stroke is approximately 41.29.

## For individuals with a stroke (t_test_stroke_1):
### P-value: 0.4417
> The p-value is greater than 0.05, indicating that there's no strong evidence of a significant difference in age between genders for individuals with a stroke.

### Effect Size (Confidence Interval):
> The confidence interval (-4.28 to 1.87) includes zero, suggesting that the true difference in means between females and males for individuals with a stroke might include zero.

### Means:
> The mean age for females with a stroke is approximately 67.30.
The mean age for males with a stroke is approximately 68.50.

## Summary:
>For individuals without a stroke, there seems to be a statistically significant difference in age between genders.

>For individuals with a stroke, there's no strong evidence of a significant difference in age between genders.

> Therefore, the results can be concluded that age and gender tend to not have a significant impact on stroke risk.

```{r}
# Assuming 'heart_disease' and 'stroke' are factors
brain_stroke$hypertension <- factor(brain_stroke$hypertension, levels = c("0", "1"))
brain_stroke$stroke <- factor(brain_stroke$stroke, levels = c("0", "1"))

# Create a summary table for counts
summary_table <- brain_stroke %>%
  group_by(hypertension, stroke) %>%
  summarise(count = n(), .groups = "drop")

# Bar plot with counts on top and custom labels
ggplot(brain_stroke, aes(x = hypertension, fill = stroke)) +
  geom_bar(position = "dodge") +
  geom_text(data = summary_table, 
            aes(x = hypertension, y = count, label = count, group = stroke),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  scale_fill_manual(values = c("grey", "red"), 
                    labels = c("No Stroke", "Stroke"),
                    name = "Stroke") +
  scale_x_discrete(labels = c("No Hypertension", "Hypertension"),
                   name = "Hypertension") +
  labs(title = "Relationship Between Hypertension and Stroke",
       x = "",
       y = "Count") +
  theme_minimal()
```

```{r}
# Assuming 'heart_disease' and 'stroke' are factors
brain_stroke$heart_disease <- factor(brain_stroke$heart_disease, levels = c("0", "1"))
brain_stroke$stroke <- factor(brain_stroke$stroke, levels = c("0", "1"))

# Create a summary table for counts
summary_table <- brain_stroke %>%
  group_by(heart_disease, stroke) %>%
  summarise(count = n(), .groups = "drop")

# Bar plot with counts on top and custom labels
ggplot(brain_stroke, aes(x = heart_disease, fill = stroke)) +
  geom_bar(position = "dodge") +
  geom_text(data = summary_table, 
            aes(x = heart_disease, y = count, label = count, group = stroke),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  scale_fill_manual(values = c("grey", "red"), 
                    labels = c("No Stroke", "Stroke"),
                    name = "Stroke") +
  scale_x_discrete(labels = c("No Heart Disease", "Heart Disease"),
                   name = "Heart Disease") +
  labs(title = "Relationship Between Heart Disease and Stroke",
       x = "",
       y = "Count") +
  theme_minimal()
```

```{r}
# Calculate the counts for each combination of hypertension and heart_disease
counts <- brain_stroke %>%
  count(hypertension, heart_disease, stroke) %>%
  group_by(hypertension, stroke) %>%
  mutate(perc = n / sum(n))

# Plot 2: Proportion of Heart Disease within Hypertension Categories by Stroke Status
ggplot(brain_stroke, aes(x = hypertension, fill = heart_disease)) +
  geom_bar(position = "fill") +
  geom_text(data = counts, aes(label = scales::percent(perc), y = perc), 
            position = position_fill(vjust = 0.5), size = 3) +
  scale_fill_manual(values = c("No Heart Disease" = "grey", "Heart Disease" = "orange")) +
  facet_grid(~ stroke) +
  labs(title = "Proportion of Heart Disease within Hypertension Categories by Stroke Status",
       x = "Hypertension",
       y = "Proportion",
       fill = "Heart Disease Status") +
  theme_minimal()
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```